Dynamical modeling of tidal streams

### 2013-12-26 tex/ms.tex
streams: some figure captions

\subsection{A simulation}\label{eq:sim}

@@

\begin{figure}[t!]
  \includegraphics[width=0.5\textwidth,clip=]{gd1_evol_xz.ps}
  \caption{}\label{fig:gd1_xy}
%python plot_stream.py ../tex/gd1_evol_xz.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaoroz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaraz.ps}\\
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjp.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaorop.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaarap.ps}
  \caption{}\label{fig:gd1_jt}
%python plot_stream.py ../tex/gd1_evol_aajrjz.ps
%python plot_stream.py ../tex/gd1_evol_aaoroz.ps
%python plot_stream.py ../tex/gd1_evol_aaaraz.ps
%python plot_stream.py ../tex/gd1_evol_aajrjp.ps
%python plot_stream.py ../tex/gd1_evol_aaorop.ps
%python plot_stream.py ../tex/gd1_evol_aaarap.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timeshist.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timesdO.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timesda.ps}
  \caption{}\label{fig:gd1_times}
%python plot_stream.py ../tex/gd1_evol_timeshist.ps
%python plot_stream.py ../tex/gd1_evol_timesdO.ps
%python plot_stream.py ../tex/gd1_evol_timesda.ps
\end{figure}

>>>>

\subsection{A simulation}\label{sec:sim}

@@

\begin{figure}[t!]
  \includegraphics[width=0.5\textwidth,clip=]{gd1_evol_xz.ps}
  \caption{Mock tidal stream simulated as described in
    \sectionname~\ref{sec:sim} after $5.01\Gyr$ of evolution in
    Galactocentric $X$ and $Z$ coordinates. The grey dot shows the
    current position of the progenitor cluster and the dashed line
    shows its orbit. The solid line gives the stream track, calculated
    using the method described in \sectionname~\ref{sec:track}. The
    inset shows a zoomed-in version of part of the leading stream that
    more clearly shows the offset between the stream track and the
    progenitor orbit.}\label{fig:gd1_xy}
%python plot_stream.py ../tex/gd1_evol_xz.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaoroz.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaaraz.ps}\\
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aajrjp.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaorop.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_aaarap.ps}
  \caption{Simulated tidal stream from \sectionname~\ref{sec:sim}
    after $5.01\Gyr$ of evolution in action--frequency--angle
    coordinates. The top row displays projections of the actions
    (left), frequencies (middle), and angles (right) in the $R$ and
    $Z$ directions; the bottom panels shows the same for $R$ and
    $\phi$. While the action distribution has a quite complicated
    form, the frequency distribution is close to one-dimensional and
    the leading and trailing parts of the stream clearly separate. In
    the right panels, the angles of the progenitor have each been
    shifted to $\pi$ and the dashed lines show the direction of the
    progenitor's frequency vector. The misalignment between the
    progenitor's frequency vector and the mean frequency vector of the
    debris is $0.18^\circ$.}\label{fig:gd1_jt}
%python plot_stream.py ../tex/gd1_evol_aajrjz.ps
%python plot_stream.py ../tex/gd1_evol_aaoroz.ps
%python plot_stream.py ../tex/gd1_evol_aaaraz.ps
%python plot_stream.py ../tex/gd1_evol_aajrjp.ps
%python plot_stream.py ../tex/gd1_evol_aaorop.ps
%python plot_stream.py ../tex/gd1_evol_aaarap.ps
\end{figure}

\begin{figure}[t!]
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timeshist.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timesdO.ps}
  \includegraphics[width=0.32\textwidth,clip=]{gd1_evol_timesda.ps}
  \caption{Properties of the simulated tidal stream of
    \sectionname~\ref{sec:sim} as a function of time. Stripping times
    are calculated by linear regression of the angle difference
    between a stream particle and the progenitor versus the equivalent
    frequency difference. The distribution of stripping times is shown
    in the left panel.  While the stripping process happens in bursts
    with a period of roughly $40\Myr$ (the radial period of the
    progenitor), it can be approximated as constant (more
    coarsely-binned solid histogram). The magnitude of the frequency
    offset between stream particles and the progenitor is shown in the
    middle panel. While particles stripped at pericenter have larger
    frequency offsets than those between pericenter passages, there is
    no secular trend and the typical frequency offset (averaged over a
    radial period) can be considered constant with time. The right
    panel shows the magnitude of the angle offset between stream
    particles and the progenitor as a function of stripping
    time. There is a spread in the angle offset at all stripping times
    because of the dispersion in frequency offsets, but typically
    stars that have been stripped earlier reach larger angle
    offsets. That is, self-sorting happens only to a small
    degree.}\label{fig:gd1_times}
%python plot_stream.py ../tex/gd1_evol_timeshist.ps
%python plot_stream.py ../tex/gd1_evol_timesdO.ps
%python plot_stream.py ../tex/gd1_evol_timesda.ps
\end{figure}
